Positional entropy, conditional entropy and mutual information in English CHILDES corpora

### 2018-09-25 english_unigram&ce&mi.Rmd
Added non-English slope bootstrapping

Get utterances
```{r get_utterances}
prov_utterances <- get_utterances(corpus = "Providence")

brown_utterances <- get_utterances(corpus = "Brown")
```

bootstrap entropy slopes
```{r slope bootstrapping}
lengths <- brown_utterances %>%
  filter(speaker_role  != "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1)

tokens <- lengths %>% 
  filter(length >= 6) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n())

#extract tokens to be used for slope bootstrapping
extract_tokens <- function(role, min_length, utterances) {
if (role == "child") {
lengths <- utterances %>%
  filter(speaker_role == "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1)

@@

@@

mid_slope <- function(df) {

@@

start_time <- Sys.time()
samples <- replicate(1000, mid_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

@@

samples %>%
  summarise(mean = mean(value), ci_upper = quantile(value, .975), 
            ci_lower = quantile(value, .025))

>>>>

Get utterances
```{r get_utterances}
prov_utterances <- get_utterances(corpus = "Providence") #stem or gloss

brown_utterances <- get_utterances(corpus = "Brown") #stem or gloss

shiro_utterances <- get_utterances(corpus = "Shiro") #use gloss

wagner_utterances <- get_utterances(corpus = "Wagner") #use gloss

okayama_utterances <- get_utterances(corpus = "Okayama") #use gloss

zhou_utterances <- get_utterances(corpus = "ZhouDinner") #use stem, NOT gloss
```

bootstrap entropy slopes
```{r slope bootstrapping}

#extract tokens to be used for slope bootstrapping
extract_stem_tokens <- function(role, min_length, utterances) {

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)

@@

extract_gloss_tokens <- function(role, min_length, utterances) {

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(gloss, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

@@

#note this measurement only makes sense if utterance length is at least 6
mid_slope <- function(df) {

@@

get_slopes <- function(role, min_length, utterances, stemgloss) {

  if (stemgloss == "stem") {
    tokens <- extract_stem_tokens(role, min_length, utterances)  
  } else {
    tokens <- extract_gloss_tokens(role, min_length, utterances)
  }

  start_slopes <- replicate(1000, start_slope(tokens)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))

  second_slopes <- replicate(1000, second_slope(tokens)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))

  mid_slopes <- replicate(1000, mid_slope(tokens)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))

  penult_slopes <- replicate(1000, penult_slope(tokens)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))

  end_slopes <- replicate(1000, end_slope(tokens)) %>% 
    as_data_frame() %>%
    summarise(mean = mean(value), ci_upper = quantile(value, .975), 
              ci_lower = quantile(value, .025))

  rbind(start_slopes, second_slopes, mid_slopes, penult_slopes, end_slopes)
}

shiro_slopes <- get_slopes("child", 6, shiro_utterances, "gloss") #what we would expect
shiro_slopes <- get_slopes("not child", 6, shiro_utterances, "gloss")
wagner_slopes <- get_slopes("child", 6, wagner_utterances, "gloss")

start_time <- Sys.time()
samples <- replicate(1000, start_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

@@

start_slopes <- samples %>%
  summarise(mean = mean(value), ci_upper = quantile(value, .975), 
            ci_lower = quantile(value, .025))
